The Astropy Project

### 2017-11-13 main.tex
misc cleanup (tab->spaces, \python, ...)

\begin{itemize}
   \item The goal is to produce a brief and informative paper that covers major
        \astropy principles not mentioned in the first paper, the core v2.0
        package, and infrastructure in \astropy project to support development
        in \python.
    \item We don't plan on including code in this paper, but if you think you
        will need to include code in your section, please add it to a separate
        Python module (.py file) and include it in this repository.
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename}
        not ``Figure''
    \item Use \escapecmd{\astropypkg} for the astropy package,
        \escapecmd{\astropy} for the astropy project, \escapecmd{\python} not
        ``Python''
    \item If your subpackage was included in Paper I, then please just include a
        note on what the package does, a reference to paper I, and any new major
        updates to your package
    \item If your subpackage was not included, then please describe the
        subpackage on level with what was in the first paper, and highlight any
        major features in it. Typical length should be equivalent to one page
        (single-column).
    \item Please make sure you are logged into Overleaf or pushing a commit with
        your information to be able to track the contributors to the paper.

@@

From its inception, \astropy has required coordination to ensure the project as a whole and its coding efforts are consistent and reasonably efficient.
While many Python projects adopt a ``Benevolent Dictator For Life'' (BDFL) model, \astropy has instead opted for a \emph{coordination committee}.
This is in part due to the nature of the project as a large-scale collaboration between many contributors with many interests, and in part due to simply the amount of work that needs to get done.
In part for the latter reason, the project has expanded the committee from three to four members starting in 2016.

@@

The \astropypkg core package is available from several of the Python distributions for scientific
% * <mattwcraig@gmail.com> 2017-10-27T07:13:51.093Z:
%
% > \astropypkg i
% I changed a few of the macros in here to refer to the package rather than the project because it is the package being discussed here.
%
% ^.
computing, such as Anaconda or Enthought Canopy, which include also some of
\astropy's affiliated packages.
Alternatively, \astropypkg can be readily installed from the Python Package
Index\footnote{\url{https://pypi.python.org/pypi}} (PyPI) using pip, the
recommended command-line tool for installing Python packages
that is included by default since Python 2 $\geq$ 2.7.9 and Python 3 $\geq$ 3.4.
For most recent \astropypkg releases, pre-built wheel distributions are obtainable
from PyPI for Windows, Mac OS X and Linux systems that provide faster
installation compared to the source distribution.  Optionally, the version of
the package and the dependencies needed to run or build the software are given
by a specifier to the pip package manager as described in PEP 440\footnote{For
more detailed installation instructions and optional flags see
\url{http://docs.astropy.org/en/stable/install.html\#installing-astropy}}.

@@

    \item [Enhanced CSV format ]

@@

		The \package{astropy.io.ascii} module now includes a significantly faster
		Cython/C engine for reading and writing ASCII files. This is available
		for the following formats: basic, commented\_header, csv, no\_header,
		rdb, and tab.  On average the new engine is about 4 to 5 times faster
		than the corresponding pure-Python implementation, and is often
		comparable to the speed of the pandas ASCII file interface. The fast
		reader has parallel processing option that allows harnessing multiple
		cores for input parsing to achieve even greater speed gains.

		By default, read() and write() will attempt to use the fast C engine when
		dealing with compatible formats. Certain features of the full read / write
		interface are not available in the fast version, in which case the
		pure-Python version will automatically be used.

@@

The documentation for many Python packages the core \package{astropy} package
as well as for all packages in the Astropy ecosystem is written using the
Sphinx package. This package makes it possible to write the documentation using
plain text files that follow a markup language called reStructuredText, and
Sphinx can then transform this into HTML or \LaTeX{} documentation. As part of
the project, we have developed a few extensions that facilitate generating
documentation for a large project like Astropy. One of the main extensions we
have developed is
\package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}},
which makes it easy with a single reStructuredText command to generate a set of
documentation pages listing all the available classes, functions, and
attributes in any given Python module.

@@

\software{\package{astropy} (\citealt{astropy}),
          \package{numpy} (\citealt{numpy}),
          \package{scipy} (\citealt{scipy}),
          \package{matplotlib} (\citealt{matplotlib}),
          \package{Cython}(\citealt{cython}),
          }

>>>>

\begin{itemize}
   \item The goal is to produce a brief and informative paper that covers major
        \astropy principles not mentioned in the first paper, the core v2.0
        package, and infrastructure in \astropy project to support development
        in \python.
    \item We don't plan on including code in this paper, but if you think you
        will need to include code in your section, please add it to a separate
        \python module (.py file) and include it in this repository.
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename}
        not ``Figure''
    \item Use \escapecmd{\astropypkg} for the astropy package,
        \escapecmd{\astropy} for the astropy project, \escapecmd{\python} not
        ``Python''
    \item If your subpackage was included in Paper I, then please just include a
        note on what the package does, a reference to paper I, and any new major
        updates to your package
    \item If your subpackage was not included, then please describe the
        subpackage on level with what was in the first paper, and highlight any
        major features in it. Typical length should be equivalent to one page
        (single-column).
    \item Please make sure you are logged into Overleaf or pushing a commit with
        your information to be able to track the contributors to the paper.

@@

From its inception, \astropy has required coordination to ensure the project
as a whole and its coding efforts are consistent and reasonably efficient.
While many \python projects adopt a ``Benevolent Dictator For Life'' (BDFL)
model, \astropy has instead opted for a \emph{coordination committee}.  This
is in part due to the nature of the project as a large-scale collaboration
between many contributors with many interests, and in part due to simply the
amount of work that needs to get done.  In part for the latter reason, the
project has expanded the committee from three to four members starting in
2016.

@@

The \astropypkg core package is available from several of the \python distributions for scientific
% * <mattwcraig@gmail.com> 2017-10-27T07:13:51.093Z:
%
% > \astropypkg i
% I changed a few of the macros in here to refer to the package rather than the project because it is the package being discussed here.
%
% ^.
computing, such as Anaconda or Enthought Canopy, which include also some of
\astropy's affiliated packages.
Alternatively, \astropypkg can be readily installed from the Python Package
Index\footnote{\url{https://pypi.python.org/pypi}} (PyPI) using pip, the
recommended command-line tool for installing \python packages
that is included by default since \python 2 $\geq$ 2.7.9 and \python 3 $\geq$ 3.4.
For most recent \astropypkg releases, pre-built wheel distributions are obtainable
from PyPI for Windows, Mac OS X and Linux systems that provide faster
installation compared to the source distribution.  Optionally, the version of
the package and the dependencies needed to run or build the software are given
by a specifier to the pip package manager as described in PEP 440\footnote{For
more detailed installation instructions and optional flags see
\url{http://docs.astropy.org/en/stable/install.html\#installing-astropy}}.

@@

    \item [Enhanced CSV format]

@@

        The \package{astropy.io.ascii} module now includes a significantly faster
        Cython/C engine for reading and writing ASCII files. This is available
        for the following formats: basic, commented\_header, csv, no\_header,
        rdb, and tab.  On average the new engine is about 4 to 5 times faster
        than the corresponding pure-\python implementation, and is often
        comparable to the speed of the pandas ASCII file interface. The fast
        reader has parallel processing option that allows harnessing multiple
        cores for input parsing to achieve even greater speed gains.

        By default, \texttt{read()} and \texttt{write()} will attempt to use
        the fast C engine when dealing with compatible formats. Certain
        features of the full read / write interface are not available in the
        fast version, in which case the pure-\python version will automatically
        be used.

@@

The documentation for many \python packages the core \package{astropy} package
as well as for all packages in the Astropy ecosystem is written using the
Sphinx package. This package makes it possible to write the documentation using
plain text files that follow a markup language called reStructuredText, and
Sphinx can then transform this into HTML or \LaTeX{} documentation. As part of
the project, we have developed a few extensions that facilitate generating
documentation for a large project like Astropy. One of the main extensions we
have developed is
\package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}},
which makes it easy with a single reStructuredText command to generate a set of
documentation pages listing all the available classes, functions, and
attributes in any given \python module.

@@

\software{\package{astropy} (\citealt{astropy}),
          \package{numpy} (\citealt{numpy}),
          \package{scipy} (\citealt{scipy}),
          \package{matplotlib} (\citealt{matplotlib}),
          \package{Cython} (\citealt{cython}),
          }
